6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
Removed all wrong references

    The reliability of the tool has steadily improved due to the iterative, generally test driven development process. A number of issues were fixed in the actual testing phase, but these were generally minor issues which did not affect the reliability of the tool directly. \ref{}

@@

        Discussed further in \ref{}

@@

        Details of the testing strategy appear in the testing section. Evidence of unit testing as well as achieved test coverage reports are available here \ref{}.

>>>>

    The reliability of the tool has steadily improved due to the iterative, generally test driven development process. A number of issues were fixed in the actual testing phase, but these were generally minor issues which did not affect the reliability of the tool directly.

@@

        As previously discussed, Riemann can handle up to 200,000 events/sec, the overwhelming majority of events will not be forwarded to the management API\@. The management API is the limiting factor, and is able to handle approximately 20 forwarded events/sec, where the request rate exceeds this, events will simply be queued. Therefore, the system is scalable well beyond the target point.

@@

        Details of the testing strategy appear in the testing section. The unit tested services achieved between 85-95\% of coverage. Evidence of unit testing as well as achieved test coverage reports are available in the code listing.
